{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-17 paper/paper.tex
use package nameref
added comment about when a scheduler is secure
package asmth was in conflict with theorem
corrected spelling

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{bussproofs}
\usepackage{amsthm}

\theoremstyle{definition}
\pagestyle{plain}
\bibliographystyle{alpha}

@@

\begin{theorem}
If the scheduler is secure and $se, \mathcal{S} \vdash P$, then P is noninterfering
\end{theorem}

>>>>

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{bussproofs}
\usepackage{nameref}

\pagestyle{plain}
\bibliographystyle{alpha}

@@

\begin{theorem}
If the scheduler is secure and $se, \mathcal{S} \vdash P$, then P is noninterfering.
\end{theorem}

The scheduler is secure, if it is defined w.r.t. the conditions from section \ref{sec:syntaxsemantics}.
